---
title: "Generate badges"
format: 
  html:
    self-contained: true
---


# data-pipelines

## Structure

* Code: [openpharma/generate_badges](https://github.com/openpharma/generate_badges)
* Rendered run: [rinpharma.github.io/data-pipelines/](https://openpharma.github.io/generate_badges/)
* Output: Direct links below. Stored in gh-pages branch

## Rebuilding

This data (and this page) rebuild automatically based on the [CRON schedule specified in the github action](https://github.com/openpharma/generate_badges/blob/main/.github/workflows/pipeline.yml#L5).

Run the pipeline with `targets::tar_make()`

Check the pipeline with `targets::tar_manifest(fields = all_of("command"))`

Visualise the pipeline with `targets::tar_visnetwork()`

```{r, results = "asis", echo = FALSE, warnings = FALSE}
cat(c("```{mermaid}", targets::tar_mermaid(), "```"), sep = "\n")
```

## Output

The current files are available

* [data.parquet](output/data.parquet)

```{r}
arrow::read_parquet(
  "https://openpharma.github.io/generate_badges/output/data.parquet"
  ) |>
  dplyr::glimpse()
```

